\theseminartitle \\ \small \thetitle

### 2021-09-12 tex/paper.tex
Minor additions to paper draft

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}

@@

\ifgerman{
	\usepackage[ngerman]{babel}
	\usepackage{ngerman}
	\usepackage{bibgerm}        % German symbols in BibTeX
}{
	\usepackage[english]{babel}
}

@@

\section{System Benchmarking}
The term "Benchmark" is a rather broad term that can be interpeted and defined in many different ways depending on the context and application domain. We will use this chapter to give a definition of Benchmarking how we will use it throughout this paper.

\subsection{Definition}
In standard literature a benchmark is commonly defined as "a tool coupled with a methodology for the evaluation and comparison of systems or components with respect to specific characteristice, such as performance, reliability or security." (\cite{sysbench} p. 4).

\subsection{Classification of Benchmarks}

\subsection{Evaluating Benchamrks}

@@

	%*********************************************************************%
	% LITERATURE                                                          %
	%*********************************************************************%
	% As a recommendation JabRef might be a usefull tool for this section. Use myRefs.bib therefore

\end{document}

>>>>

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{hyperref}

@@

\usepackage[english]{babel}

@@

\section{System Benchmarks}
\label{sec:benchmarking}
The term "Benchmark" is a broad term that can be interpeted and defined in many different ways depending on the context and application domain. We will use this chapter to give a definition of Benchmarking how we will use it throughout this paper.

\subsection{Definition}
\label{ssec:bench_definition}
The term "Benchmark" is used in a variaty of different domains and, according to the Standard Specialization Evalutation Corporation, historically stems from a physical marking that was used as a refernce point on a workbench to check the length of the produced pieces\footnote{SPEC Glossary: \url{https://www.spec.org/spec/glossary/\#benchmark}}. However throughout this paper we are only interested in system benchmarks within the context of software systems and will therefore also refer to the definition of a benchmark as given by Kounev et al.: "a tool coupled with a methodology for the evaluation and comparison of systems or components with respect to specific characteristics, such as performance, reliability or security." (\cite{Kounev} p. 4). As already given from this definition benchmarks can serve as an evaluation for different characteristics. We will more closely look at these in \autoref{ssec:bench_classification}. Throughout this paper we will also mostly refer to the "system or component" that is being benachmarked as the \textit{System under Test} (SUT).

\subsection{Classification of Benchmarks}
\label{ssec:bench_classification}

\subsection{Evaluating Benchmarks}

@@

	%*********************************************************************%
	% LITERATURE                                                          %
	%*********************************************************************%
	% As a recommendation JabRef might be a usefull tool for this section. Use myRefs.bib therefore
	\phantomsection
	\bibliographystyle{splncs03}
	\bibliography{literature}	
\end{document}
